\documentclass{article}
\usepackage[left=1cm,right=1cm,top=1cm,bottom=1cm]{geometry}
\usepackage{longtable}
\setlength{\parindent}{0pt}

\begin{document}
    \pagenumbering{gobble}
    \section*{Vasily Ermakov\\Back-end software engineer}
    6 years as a Java back-end software engineer. 9 month as an application architect.\\
    Experienced in banking, financial, healthcare \& business automation domains.\\
    Interested in distributed systems, software architecture \& design and functional programming.\\
    \begin{tabular}{p{275pt} p{275pt}}
        \section*{Contacts}
        Email - vasia.ermakov@gmail.com

        LinkedIn - linkedin.com/in/vasily-ermakov

        Github - github.com/vasily-ermakov
        &
        \section*{Languages}
        English - Fluent

        Russian - Native

        German - Beginner

        Dutch - Beginner\\
        \section*{Education}

        Belarusian State University, 2017

        Bachelor's degree, Mathematics and Computer Science

        Faculty of Applied Mathematics and Computer Science

        Department of Discrete Mathematics and Algorithmics
        &
        \section*{Technology stack}
        Java, Spring Framework, Hibernate ORM, OpenAPI

        Haskell

        SQL, Relational databases, Liquibase

        Git

        Apache Maven, Gradle Build Tool\\
        \section*{Certifications}
        Oracle Certified Professional, Java SE 8 Programmer, 2019

        Oracle Certified Associate, Java SE 8 Programmer, 2018

        Haskell functional programming, Stepik, 2019
        &
        \section*{Industry knowledge}
        OOP, design patterns, functional programming

        Domain-driven design

        Microservices, CI/CD

        Unit and integration testing

        Agile methodologies

        Algorithm analysis \& design

        Graph theory, discrete mathematics

        Touch typing
    \end{tabular}
    \section*{Experience}
    \begin{longtable}{l p{450pt}}
        2022-02 - present & Back-end software engineer, Specific-Group Lithuania

        Core banking and payment system integration via ISO 8583.

        Responsibilities:
        \begin{itemize}
            \item application skeleton configuration (database schema migration, API code generation);
            \item code style definition;
            \item estimation;
            \item code review;
            \item mentorship;
            \item interviewing;
            \item unit test coverage;
            \item reconciliation and post transaction business processes implementation;
            \item payment system integration.
        \end{itemize}

        Technologies \& tools: Java SE 17, Spring Boot, Hibernate ORM, Oracle Database, OpenAPI, Keycloak, Prometheus, Postman, SonarQube, OpenShift.
        \\[8pt]
        2021-04 - 2022-03 & Back-end software engineer, Specific-Group Lithuania

        GDPR consent withdrawal orchestration

        Description: customer personal data consent withdrawal orchestration.

        Responsibilities:
        \begin{itemize}
            \item application skeleton configuration (database schema migration, API code generation, integration testing);
            \item code style definition;
            \item estimation;
            \item code review;
            \item unit and integration test coverage;
            \item parallel processing implementation;
            \item authorization configuration;
            \item application metrics exposure;
            \item Postman collection preparation.
        \end{itemize}
        Technologies \& tools: Java SE 11, Spring Boot, Hibernate ORM, Oracle Database, H2, OpenAPI, Keycloak, Prometheus, Postman, Thymeleaf, SonarQube, OpenShift.
        \\[8pt]
        2021-01 - 2021-04 & Back-end software engineer, Specific-Group Lithuania

        Wealth management platform

        https://wealthpilot.com/

        Responsibilities:
        \begin{itemize}
            \item industry dimension implementation;
            \item performance optimization;
            \item integration test coverage.
        \end{itemize}
        Technologies \& tools: Java SE 11, Spring Boot, Hibernate ORM, Oracle Database, Gradle Build Tool, Liquibase.
        \\[8pt]
        2020-01 - 2020-10 & Application architect, Specific-Group

        Customer appointment with adviser scheduling

        Responsibilities:
        \begin{itemize}
            \item application architecture;
            \item microservice, microservice parent \& configuration server archetyping;
            \item code style definition;
            \item code review;
            \item business analyst interaction via user stories;
            \item splitting user stories into technical tasks;
            \item DevOps interaction;
            \item mentorship.
        \end{itemize}
        Technologies \& tools: Java SE 8, Apache Maven, Spring Boot, Hibernate ORM, OpenAPI, Microsoft Graph API, Keycloak, JUnit 5, Postman.
        \\[8pt]
        2019-05 - 2021-01 & Back-end software engineer, Specific-Group

        Building society

        https://www.start-bausparkasse.at/start-bausparkasse/ueberuns/start-bausparkasse

        Responsibilities:
        \begin{itemize}
            \item Common Reporting Standard (Standard im Gemeinsamen Meldestandard-Gesetz) implementation;
            \item Data Protection Laws and Regulations compliance;
            \item Microsoft Azure migration;
            \item monitoring automation;
            \item mentorship.
        \end{itemize}
        Technologies \& tools: Java SE 8, Spring Boot, Hibernate ORM, Oracle Database, PostgreSQL, Flyway, Gradle Build Tool, OpenAPI, Postman, WSO2, Kong Gateway.
        \\[8pt]
        2018-08 - 2019-04 & Back-end software engineer, Specific-Group

        PSD2 enabler

        https://www.coconet.de/en/regulatory/psd2.html
        \\[8pt]
        2018-05 - 2019-04 & Back-end software engineer, Specific-Group

        Reusable cups business automation

        https://www.cupsolutions.at/faq/mycoffeecup/
        \\[8pt]
        2018-04 - 2018-08 & Full-stack software engineer, Specific-Group

        Office presence monitoring
        \\[8pt]
        2017-09 - 2018-05 & Back-end software engineer, Specific-Group

        Tax adviser accounting digitization
        \\[8pt]
        2017-05 - 2017-09 & Full-stack software engineer, Specific-Group

        Report generator
        \\[8pt]
        2014-09 - 2015-09 & Back-end software engineer, Exadel

        Document routing

        https://exadel.com/portfolio/ghx
        \\[8pt]
        2012-09 - 2014-05 & Mathematics olympiads trainer, Gymnasium 56
    \end{longtable}
\end{document}
